GRASS GIS crowdsourcing of the local calibration of ETa models to improve on public domain Global ET products

### 2013-04-19 grasslecture/20130416_Trento_G7/crowdsourceET.tex
Final version from the FEM talk
git-svn-id: https://svn.osgeo.org/grass/grass-promo@55905 15284696-431f-4ddb-bdfa-cd5b030d7da7

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]{Chain processing}

@@

@@

\subsection{Year 1}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]{set up for year 1: Kick the geek}

@@

\subsection{Year 2}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]{set up for year 2: Bring the bee}

@@

\subsection{Year 3}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]{set up for year 3: Ubergeek upgrade}

>>>>

\subsection{Blueprint}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]{Blueprint}

\begin{center}
 \includegraphics[width=8cm]{chain0}
\end{center}

\begin{itemize}
 \item GDAL+[C+OpenMP]
 \item GRASSGIS+pyGRASS+[C+OpenMP]
\end{itemize}

\subsection{GDAL}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]{HPC GDAL framework}

\begin{columns}[l]
\column[t]{0.6\textwidth}
\begin{center}
 GDAL+[C+OpenMP]
 \includegraphics[width=7.5cm]{chain2}
\end{center}
\column[t]{0.4\textwidth}
\begin{center}
 OpenMP distribution
 \includegraphics[width=5cm]{chain1}
\end{center}
\end{columns}
\end{frame}

\subsection{GRASS GIS}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]{GRASS GIS framework}

\begin{center}
 \includegraphics[width=7.5cm]{architecture_implementation}
\end{center}

\begin{block}{metaModule concept}
{\bf pyGRASS:} vertical integration of GRASS GIS modules\\
{\bf GRASS GIS modules:} [C+OpenMP] any multi-core PC \\
{\bf GRASS GIS modules:} [C+MPIch?] in FEM - GISCluster \\
{\bf GRASS GIS modules:} [C+CUDA/GPGPU?] in FEM - Tesla
\end{block}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]{Chain processing}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]{Initial results of ET Models comparison}

\begin{center}
 Average ET for Sri Lanka, Daily 2000-2012 (mm/d, daily, 12.3 years)
 \includegraphics[width=12cm]{sltemporaletb}
\end{center}

\begin{block}{Comparison}
\begin{itemize}
 \item ETo \& ETpot (rad) are similar, expected.
 \item ETa models are not so similar, expected.
 \item ETo \& ETpot (rad) are higher than ETa models, expected.
\end{itemize}

\end{block}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]{set up for year 1: Kick the geek}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]{set up for year 2: Bring the bee}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]{set up for year 3: Ubergeek upgrade}
